---
title: 'Assignment week 2: R Markdown and Leaflet'
author: "B vStraaten"
date: "March 13, 2018"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is my submission for the Assignment of week 2 of the developing data products course. If you'd like to reproduce this maps, make sure to install the following packages.

```{r packages, message = FALSE}
library(leaflet)
library(dplyr)
library(readr)
library(randomcoloR)
```

## Data
I got some data on countries, cities and population and filtered it to only include Germany. See references for credits.

```{r data, message = FALSE}
URL <- "https://simplemaps.com/static/data/world-cities/basic/simplemaps-worldcities-basic.csv"
data <- read_csv(URL)
data <- filter(data, country == "Germany")
```

(I had to fiddle around a bit to make the colors work since the usual colorbrewer palettes do not have not colors for my factor. This little bit makes the leaflet code easier.)

```{r color}
province <- unique(data$province) # get unique provinces
n <- length(province) # get number of provinces
palette <- distinctColorPalette(n) # get colors for each province
dfcol <- data.frame(province, palette) # create df with color and province
data <- merge(data, dfcol, by = "province") # merge dfcol and data2
```

## Map
The map shows germany and it's s cities. The size of the circles show the population. The color shows the province. Click on the marker so see the population.

```{r map, message = FALSE}
my_map <- data %>%
        leaflet(width = "100%") %>%
        addTiles() %>%
        addMarkers(popup = as.character(data$pop)) %>%
        addCircles(weight = 1, radius = sqrt(data$pop)*50, color = data$palette) %>%
        addLegend(labels = unique(data$province), colors = unique(data$palette))
my_map
```


## References

* https://simplemaps.com/data/world-cities
* https://stackoverflow.com/questions/15282580/how-to-generate-a-number-of-most-distinctive-colors-in-r